AbxD01 Analysis

### 2015-01-22 abxD01_analysis.Rmd
minor changes
worked on model optimization
pats new formula for r2, new model optimization markdown file under
figure 6 including html output
Figure 1 associated stats

## Figure 1

@@

```{r, eval=FALSE}
#################################################
#Purpose: Convert csv matrix of columns you want converted into barcharts
#input: csv file following this heading format format:  sampleID, expgroup, nextDayCFU, Otu001, Otu002, Otu003, etc
#ex:file<-read.csv("~/Desktop/mothur/abxD01/barcharts/abxD01.final.tx.5.subsample.relabund.topdose.forlogscale2.csv
#Note: It is assumed that anything after the expgroup column are vectors containing data to be split by the groups in 'expgroup' 
#      and averaged with SD measured. 
#Output: matrices avg[],  std[], bp[y] with the barplot coordinates info stored for each subgraph
#################################################
# Parameters to change:
# CSV file: Group  expgroup  Otu001... (limited by most abund, end with 'Other', OTUs normalized +0.0001, expgroups #'d by graph order & sorted by first graph)
file<-read.csv("~/Desktop/mothur/abxD01/barcharts/abxD01.final.tx.1.subsample.relabund.topdose2.forlogscale.csv", header=T)
fileIDS<-read.csv("~/Desktop/mothur/abxD01/barcharts/topdose_tx1_barchart_ids.csv", header=T)
# Y Labels for each graph: 
abx<-c("Untreated", "Ciprofloxacin", "Clindamycin", "Vancomycin", "Streptomycin", "Cefoperazone", "Ampicillin", "Metronidazole")

@@

>>>>

## Figure 1: Bargraph

@@

```{r, eval=FALSE}
#################################################
#Purpose: Convert csv matrix of columns you want converted into barcharts
#input: csv file following this heading format format:  sampleID, expgroup, nextDayCFU, Otu001, Otu002, Otu003, etc
#ex:file<-read.csv("~/Desktop/mothur/abxD01/barcharts/abxD01.final.tx.5.subsample.relabund.topdose.forlogscale2.csv
#Note: It is assumed that anything after the expgroup column are vectors containing data to be split by the groups in 'expgroup' 
#      and averaged with SD measured. 
#Output: matrices avg[],  std[], bp[y] with the barplot coordinates info stored for each subgraph
#################################################
# Parameters to change:
# CSV file: Group  expgroup  Otu001... (limited by most abund, end with 'Other', OTUs normalized +0.0001, expgroups #'d by graph order & sorted by first graph)
file<-read.csv("/Documents/Github/abxD01/Figure 1/abxD01.final.tx.1.subsample.relabund.topdose2.forlogscale.csv", header=T)
fileIDS<-read.csv("/Documents/Github/abxD01/Figure 1/topdose_tx1_barchart_ids.csv", header=T)
# Y Labels for each graph: 
abx<-c("Untreated", "Ciprofloxacin", "Clindamycin", "Vancomycin", "Streptomycin", "Cefoperazone", "Ampicillin", "Metronidazole")

@@

### Figure 1: Statistics

To compare CFU levels: 
```{r, eval=TRUE}

file<-read.csv("~/Documents/Github/abxD01/Figure 1/abxD01.final.tx.1.subsample.relabund.topdose2.forlogscale.csv", header=T)

data <- file[ which(file$expgroup != '1untr'), ] #choose experimental groups
data$nextDayCFU<-log10(data$nextDayCFU+1) #log transform CFUs
anova(lm(data$nextDayCFU ~ data$expgroup)) #perform anova across experimental groups for CFU

#Which groups are different? Ciprofloxacin was clearly lower
data <- data[ which(data$expgroup != '2cipro'), ] #remove ciprofloxacin to see now if there's a difference in remaining groups
anova(lm(data$nextDayCFU ~ data$expgroup))

```
Alternatively:
```{r, eval=TRUE}
data<-read.csv("~/Documents/Github/abxD01/Figure 1/abxD01.final.tx.1.subsample.relabund.topdose2.forlogscale.csv", header=T)

data <- file[ which(file$expgroup != '1untr'), ] #choose experimental groups
data$nextDayCFU<-log10(data$nextDayCFU+1) #log transform CFUs
CFU.anova <- aov(nextDayCFU ~ expgroup, data = data)
CFU.tukey <- TukeyHSD(CFU.anova)

library(multcomp)
library(multcompView)
multcompLetters4(CFU.anova, CFU.tukey)
```
The CFU levels were significantly different between the ciprofloxacin treated communities and all other treatments.

Amova calculation in mothur to determine the uniqueness of each community structure:
```
dist.shared(shared=abxD01.final.an.unique_list.0.03.topdose2.shared, calc=thetayc-jclass, subsample=1625)
amova(phylip=abxD01.final.an.unique_list.0.03.topdose2.thetayc.0.03.lt.ave.dist, design=topdose_design_byABX.txt, iters=1000000)

```
This results in the file called "abxD01.final.an.unique_list.0.03.topdose2.thetayc.0.03.lt.ave.amova" located in the github folder. The results of these are summarized in "amova8expgroups.xlsx".
